EEG characterization and classification based on Histogram of Gradients of Signal Plots

### 2017-09-19 coverletter.tex
Version sent by email

We believe that this proposed method based on the histograms of gradients of signal plots, and most importantly, its successful application to identify ERP markers within EEG signals from ALS patients is relevant for this special issue and that it will contribute with a novel tool to analyse EEG signals.

>>>>

We believe that this proposed method based on the histograms of gradients of signal plots, and most importantly, its  application to identify ERP markers within EEG signals relevant for this special issue and that it will contribute with a novel tool that can be used to enhance or improve HCI systems.

We submitted previously on-time the
